---
title: "index"
output: html_document
date: '2022-05-17'
---

```{r setup, include = FALSE}
library("knitr")
source("summary.R")
source("table.R")
source("chart1.R")
source("chart2.R")
source("chart3.R")
```


### **Introduction Paragraph**

The datasets that we used was a COVID-19 dataset and a COVID Vaccination dataset. In the COVID-19 dataset, it contains data on the statistics of COVID in countries around the world. This data within this dataset has been collected since the start of the pandemic and has been generated by an organization known as Our World in Data in collaboration with the University of Oxford. The COVID Vaccination dataset has also been generated by the organization, Our World in Data, and contains the statistics of the COVID vaccination in countries around the world over time. 


### **Summary Paragraph**

From our summary of the dataset, we can see that there are `r format(summary_data_info$num_observations, scientific = FALSE, big.mark=',')` observations and `r summary_data_info$num_features` features. In the dataset, there are a total of `r format(summary_data_info$world_total_cases$total_cases, scientific = FALSE, big.mark=',')` cases and `r format(summary_data_info$world_total_deaths$total_deaths, scientific = FALSE, big.mark=',')` deaths as of `r summary_data_info$world_total_cases$date`. As of `r summary_data_info$location_max_cases$date`, the location with the most cases is `r summary_data_info$location_max_cases$location` at `r format(summary_data_info$location_max_cases$total_cases, scientific = FALSE, big.mark=',')` total cases and the location with the most deaths is `r summary_data_info$location_max_deaths$location` at `r format(summary_data_info$location_max_deaths$total_deaths, scientific = FALSE, big.mark=',')` total deaths. In the World, `r summary_data_info$world_total_tests$location` led with the most tests as there was a total of `r format(summary_data_info$world_total_tests$total_tests, scientific = FALSE, big.mark=',')` tests by `r summary_data_info$world_total_tests$date`. As of `r summary_data_info$total_vaccinations$date`, in `r summary_data_info$total_vaccinations$location`, `r format(summary_data_info$total_vaccinations$total_vaccinations, scientific = FALSE, big.mark=',')` vaccinations have been administered.


### **Table**

```{r table, echo = FALSE}
kable(rmd_report)
```
The table shows that there is a huge jump in cases between 2020-05-01 and 2020-09-01. After that the cases seem to slow down at the beginning of 2021 and afterwards it continues to increase at a fast rate. 

### **Charts**

#### Charts 1 & 2 - Maps
```{r map, warning = FALSE, echo = FALSE}
get_map(covid_data, "cases")
get_map(covid_data, "vaccinations")
``` 
In these two maps, it can be seen that the maps represent the most recent data on the total cases in the dataset. This chart shows the areas where there were the most cases. The vaccination map also shows that where the places that had the most cases also had the most vaccinations. China is an outlier among the countries with cases since they are one of most dense and highly populated countries but have a low number of cases. Places like Brazil and India are high-density with a high population with more cases. China also has high total vaccinations which shows that they are able to control the spread of COVID in their country.

#### Chart 3 - Scatter
```{r scatter, warning = FALSE, echo = FALSE}
get_scatter(covid_data)
```
This scatter plot shows the relationship between the total vaccinations per hundred and the total deaths per million in each country with each being colored by their respective continent. Towards the origin you can see a majority of African countries with a mixture of countries from Oceania and Asia. As you get further away from the origin, it becomes a mixture of North America and Asia and even further out is Europe and South America. This shows that in countries that have lower total vaccinations per hundred, there is more total deaths per million and as you have more total vaccinations, the total deaths per million decreases.

#### Chart 4 - Trend
```{r trend, echo = FALSE}
get_bar(covid_data, "OWID_WRL")
```
The chart of time shows that there were spikes in deaths around January and April and May which can be a result of Christmas and New Years as well as Spring and Summer time. Christmas and New Years are times where large groups like to gather to celebrate the holidays which can lead to more cases and more deaths. In the Spring and Summer, people like to go to the beaches and outside and since this was the time where lockdowns were being lifted, everyone wanted to be outside. Towards the end of 2021 and the beginning of 2022, the graph begins to plateau.
